Supplementary material

### 2022-03-21 analysis/supplementary-materials/supplementary.Rmd
Minor edits

filter(rcarbon, site_name  == "Langangen Vestgård 5") %>% 
  select(lab_code, c14_bp, error, material, context) %>% 
   kable(caption = "Langangen Vestgård 5", col.names = c("ID",
                    "\\textsuperscript{14}C BP",
                    "Error",
                    "Material",
                    "Context"),
        booktabs = TRUE,  linesep = c(""), escape = FALSE)
```

@@

filter(rcarbon, site_name  == "Løvås 2") %>% 
  select(lab_code, c14_bp, error, material, context) %>% 
   kable(caption = "Løvås 2", col.names = c("ID",
                    "\\textsuperscript{14}C BP",
                    "Error",
                    "Material",
                    "Context"),
        booktabs = TRUE,  linesep = c(""), escape = FALSE)
```

>>>>

filter(rcarbon, site_name  == "Langangen Vestgård 5") %>% 
  select(lab_code, c14_bp, error, material, context) %>% 
   kable(caption = "Langangen Vestgård 5", col.names = c("ID",
                    "\\textsuperscript{14}C BP",
                    "Error",
                    "Material",
                    "Context"),
        booktabs = TRUE,  linesep = c(""), escape = FALSE) %>% 
  kable_styling(latex_options="scale_down")
```

@@

filter(rcarbon, site_name  == "Løvås 2") %>% 
  select(lab_code, c14_bp, error, material, context) %>% 
   kable(caption = "Løvås 2", col.names = c("ID",
                    "\\textsuperscript{14}C BP",
                    "Error",
                    "Material",
                    "Context"),
        booktabs = TRUE,  linesep = c(""), escape = FALSE) %>% 
  kable_styling(latex_options="scale_down")
```
